---
title: "homework_8"
author: "Aurna Mukherjee (am96848)"
date: "2025-04-09"
output:
  pdf_document: default
  html_document: default
---

[Link to Github](https://github.com/aurnam18/hw8)

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
library(kableExtra)
library(mosaic)
library(MatchIt)
```

# **Problem 1**

```{r echo=FALSE}
library(readr)
creatinine <- read_csv("creatinine.csv")
#Part A
lm_creatinine <- lm(creatclear ~ age, data = creatinine)
lm_creatinine
age_55 <- 55*-0.6198 + 147.8129
```

I got this value by finding the y-intercept and rate of change for the linear regression model of cleatclear and age. I used y=mx+b, plugging in 55 for x and using the constants I had for m and b.

The creatinine clearance rate decreases by 0.6198 for each year of age (-0.6198 ml/minute/year)

```{r echo=FALSE}
expected_40 <- 40*-0.6198 + 147.8129
residual_40 <- 135-expected_40

expected_60 <- 60*-0.6198 + 147.8129
residual_60 <- 112-expected_60
```

Because the residual is lower for the 60 year old, their creatinine clearance rate is better.

# **Problem 2**

```{r echo=FALSE}
covid <- read_csv("covid.csv")
covid_spain <- subset(covid, country=="Spain")
covid_italy <- subset(covid, country=="Italy")
lm_spain <- lm(log(deaths)~days_since_first_death, data=covid_spain)
lm_italy <- lm(log(deaths)~days_since_first_death, data=covid_italy)
growth_spain <- 0.276
double_spain <- round(70/0.276, 2)
boot_spain = do(10000)*lm(log(deaths)~days_since_first_death,
data=resample(covid_spain))
confint(boot_spain, level = 0.95)
growth_italy <- 0.183
double_italy <- round(70/0.183, 2)
boot_italy = do(10000)*lm(log(deaths)~days_since_first_death,
data=resample(covid_italy))
confint(boot_italy, level = 0.95) #growth rate between 0.16 and 0.21
```

The estimated growth rate for Spain is 0.276 and the doubling time is 253.62. The 95% confidence interval for the days since the first death is between 0.23 and 0.32. The estimated growth rate in Italy is 0.183 and the doubling time is 382.51. The 95% confidence interval for the days since the first death is between 0.16 and 0.21 in Italy.

```{r echo=FALSE}
ggplot(covid) + 
   geom_line(aes(x=days_since_first_death, y=deaths, color=country)) +
   labs(title = "COVID-19 Deaths Over Time by Country")
```

# **Problem 3**

```{r echo=FALSE}
milk <- read_csv("milk.csv")
lm_milk = lm(log(sales) ~ log(price), data=milk)
coef(lm_milk)

boot_milk = do(10000)*lm(log(sales) ~ log(price), data=resample(milk))
confint(boot_milk, level = 0.95) #growth rate between 0.16 and 0.21
```

Our estimated elasticity is about -1.62, meaning when the price of milk increases by 1%, people want to buy about 1.62% less of it. We are 95% sure that the price elasticity is between -1.45 and 1.77, and the way this confidence interval was calculated is through bootstrapping a linear regression model plotting log(sales) and log(price), since it represents a power law.
